---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgprompt

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/pkgprompt)](https://CRAN.R-project.org/package=pkgprompt)
<!-- badges: end -->

Information in a large language model's prompt is analogous to its short-term memory; models will provide more informative answers on problem contexts that they've been prompted on, even if the same information was in the training data. This package converts R package documentation to LLM-readable plain text to facilitate passing it as part of a prompt.
    
## Installation

You can install the development version of pkgprompt like so:

``` r
pak::pak("simonpcouch/pkgprompt")
```

## Example

Pass the name of a package to grab all of its documentation as plain text:

```{r example}
library(pkgprompt)

pkg_prompt(pkg = "splines")
```

You can optionally include only a subset of topics in the package in the results:

```{r example-topic}
pkg_prompt(pkg = "splines", topics = c("ns", "bs"))
```
